251 Rescues

### 2024-02-16 code/process.Rmd
making print better

```
# Subjective
* We will report the distribution of subjective replication success in our rescue sample

@@

irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
irr
```
* We will report the distribution of subjective replication success in our rescue sample

Of a total of `r nrow(subj)` replication, `r nrow(success)` succeeding at mostly or fully replicating the original results (`r pluck(tallied,2,1)` with a score of 0, `r pluck(tallied, 2,2)` with a score of .75, and `r pluck(tallied, 2,3)` with a score of 1). The interrater reliability was `r irr |> round(2)`.

@@

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc') |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2", font_size=40) 
#cors
```
* If there is a mixture of projects that succeed and fail to replicate the original results, we will qualitatively describe differences that may have played a role.

It looks like the ones with poor replication sample (due to inflated effect size, or exclusion/attrition/etc issues) where the rescue recruited more is the only sorta strong predictor

@@

```{r}
parsed_d |> select(target_lastauthor_year, type, N, closeness, replication_score) |> 
  filter(type!="additional") |> 
  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
  select(paper=target_lastauthor_year, replication_score=replication_score_rescue, N_original, N_rep1, N_rescue,
         closeness_rep1, closeness_rescue) |> arrange(replication_score |> desc())

@@

orig_v_others |> select(target_lastauthor_year, d_p_orig)

@@

## Secondary TODO you are here!

@@

orig_v_rescue  |> select(target_lastauthor_year, d_p_orig)

@@

orig_v_not_rescue  |> select(target_lastauthor_year, d_p_orig)

@@

rescue_v_reps |> select(target_lastauthor_year, d_p_orig)

@@

```
## predInt with heterogeneity

>>>>

# Subjective

* We will report the distribution of subjective replication success in our rescue sample

@@

irr <- cor.test(d$TA_rep_score, d$MCF_rep_score, method="spearman")$estimate
irr
```

Of a total of `r nrow(subj)` replication, `r nrow(success)` succeeding at mostly or fully replicating the original results (`r pluck(tallied,2,1)` with a score of 0, `r pluck(tallied, 2,2)` with a score of .75, and `r pluck(tallied, 2,3)` with a score of 1). The interrater reliability was `r irr |> round(3)`.

@@

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc') |> kable_styling(full_width=F, htmltable_class = "lightable-classic-2") 
#cors
```
* If there is a mixture of projects that succeed and fail to replicate the original results, we will qualitatively describe differences that may have played a role.

It looks like the ones with poor replication sample (due to inflated effect size, or exclusion/attrition/etc issues) where the rescue recruited more is the only sorta strong predictor. (I added a couple non-pre-reg'd relative sample size of rep1 measures)

@@

```{r}
parsed_d |> select(target_lastauthor_year, type, N, closeness, replication_score) |> 
  filter(type!="additional") |> 
  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
  select(paper=target_lastauthor_year, rescue_score=replication_score_rescue, N_original, N_rep1, N_rescue,
         closeness_rep1, closeness_rescue) |> arrange(rescue_score |> desc())

@@

@@

@@

@@

@@

## show p_origs

```{r}
 all <- orig_v_others |> select(target_lastauthor_year, orig_v_other=d_p_orig) |> 
  left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue=d_p_orig)) |> 
  left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue=d_p_orig)) |> 
  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps=d_p_orig)) |> 
  rename(paper=target_lastauthor_year)

all

@@

## predInt with heterogeneity
